Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-22 paper/icml_drau/advup.tex

%\TODO{CT and LB are fighting each other about the importance which should be given to the next paragraph. A impartial judge should give his opinion. (CT is wrong)}
Still, this reparameterization does not, on its own, guarantee that $A$
correctly approximates $A^\pi_\deltat$ if
$Q$ approximates $Q^\pi_\deltat$% \footnote{
% 	Ensuring that $A$ does not differ from $A^\pi_\deltat$ by a state dependent function only affects
% 	$A$'s interpretability. Indeed, for any function $f$, the ranking of actions given by
% 	$A^\pi_\deltat(s, \cdot)$ and $A^\pi_\deltat(s, \cdot) + f(s)$ is
% 	the same. \TODO{still unclear why we'd care about identifiability}
%}
.
Indeed, for any given pair $(V,\,A)$, the pair $(V(s) -
f(s),\,A(s,a)+f(s)/\deltat)$ (for an arbitrary $f$)
% \begin{align}
% 	\tilde{V}(s) &= V(s) - f(s),\qquad
% 	\tilde{A}(s, a) = A(s, a) + \frac{f(s)}{\deltat}
% \end{align}
yields the exact same $Q$ function. This new $A$ still defines %the same $Q$ and
the same ranking of actions, yet this phenomenon might cause
numerical problems or instability of $A$ when $\deltat\to 0$, and prevents direct
interpretation of the learned $A$.
% Consequently, $Q$ can correctly approximate
% $Q^\pi$ even if $A$ is arbitrarily far from $A^\pi$.
To enforce identifiability of $A$, one must enforce the consistency equation
\begin{equation}
	Q^\pi_\deltat(s, \pi(s)) - V^\pi_\deltat(s) = 0
\end{equation}
on the approximate $A$ and $V$. This translates to
\begin{equation}
	A(s, \pi(s)) = 0.
\end{equation}
With this additional constraint, if $Q = Q^\pi_\deltat$, then $A =
A^\pi_\deltat$ and $V = V^\pi_\deltat$: indeed \TODO{keep or  leave as
an exercise?}
\begin{align}
	A^\pi_\deltat(s, a) &= \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat}\\
		    &= \frac{Q(s,a) - Q(s, \pi(s))}{\deltat}\\
		    &= A(s, a).
\end{align}
In the spirit of~\cite{dueling_nets}, this condition is enforced by writing $A$ as
\begin{equation}
\label{eq:Aparam}
	A(s, a) \deq \bar{A}(s, a) - \bar{A}(s, \pi(s)).
\end{equation}
With this parameterization, one can hope to learn an approximation of $A^\pi$,
from which a proper ranking of actions can be derived for any $\deltat$.

>>>>

%\TODO{CT and LB are fighting each other about the importance which should be given to the next paragraph. A impartial judge should give his opinion. (CT is wrong)}
Still, this reparameterization does not, on its own, guarantee that $A$
correctly approximates $A^\pi_\deltat$ if
$Q$ approximates $Q^\pi_\deltat$% \footnote{
% 	Ensuring that $A$ does not differ from $A^\pi_\deltat$ by a state dependent function only affects
% 	$A$'s interpretability. Indeed, for any function $f$, the ranking of actions given by
% 	$A^\pi_\deltat(s, \cdot)$ and $A^\pi_\deltat(s, \cdot) + f(s)$ is
% 	the same. \TODO{still unclear why we'd care about identifiability}
%}
.
Indeed, for any given pair $(V,\,A)$, the pair $(V(s) -
f(s),\,A(s,a)+f(s)/\deltat)$ (for an arbitrary $f$)
% \begin{align}
% 	\tilde{V}(s) &= V(s) - f(s),\qquad
% 	\tilde{A}(s, a) = A(s, a) + \frac{f(s)}{\deltat}
% \end{align}
yields the exact same $Q$ function. This new $A$ still defines %the same $Q$ and
the same ranking of actions, yet this phenomenon might cause
numerical problems or instability of $A$ when $\deltat\to 0$, and prevents direct
interpretation of the learned $A$.
% Consequently, $Q$ can correctly approximate
% $Q^\pi$ even if $A$ is arbitrarily far from $A^\pi$.
To enforce identifiability of $A$, one must enforce the consistency equation
\begin{equation}
	Q^\pi_\deltat(s, \pi(s)) - V^\pi_\deltat(s) = 0
\end{equation}
on the approximate $A$ and $V$. This translates to
\begin{equation}
	A(s, \pi(s)) = 0.
\end{equation}
With this additional constraint, if $Q = Q^\pi_\deltat$, then $A =
A^\pi_\deltat$ and $V = V^\pi_\deltat$: indeed \TODO{keep or  leave as
an exercise?}
\begin{align}
	A^\pi_\deltat(s, a) &= \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat}\\
		    &= \frac{Q(s,a) - Q(s, \pi(s))}{\deltat}
		    %\\ &
		    = A(s, a).
\end{align}
In the spirit of~\cite{dueling_nets}, this condition is enforced by
parameterizing $A$ through another function $\bar{A}$ and setting
\begin{equation}
\label{eq:Aparam}
	A(s, a) \deq \bar{A}(s, a) - \bar{A}(s, \pi(s)).
\end{equation}

This approach will lead to $\deltat$-robust algorithms for
approximating $A^\pi$, from which a ranking of actions can be
derived.
